Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex
removed yellow bg

% heather - add more results in here since we have more to report. Probably cut down image manipulation?
\begin{abstract}
We introduce \textit{Rewind}, a system that assists in the recall of semantic and episodic memory by automatically recreating interactive sceneries of past trips. \textit{Rewind} uses historical geolocation data to generate egocentric videos of earlier experiences from publicly-available street side images. Since the effectiveness of memory cues is determined by their level of integration with the target memory, images used in \textit{Rewind} are manipulated to incorporate time-of-day, seasonal and weather information, thereby creating more faithful representation of the original experience. Users can interactively go back and forth in time by scrubbing over the video. Together, the composed \textit{Rewind} videos offer users a window into past travels. We report the results of a user study with eighteen participants conducted to collect location data over two weeks. Trips taken in groups were more likely to be recalled using \textit{Rewind} videos than trips taken alone. \textit{Rewind} also serves as an experiment of the extreme scenario where users can freely roam and experience the world, keeping their mobile devices in their pockets, and still preserve believable representations that capture the past.
\end{abstract}

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 19 & 67 & 61 & 25 & \cellcolor[HTML]{ACDDAA}71 & \cellcolor[HTML]{ACDDAA}11 & 5 & 5 & 13 & 30 & 32 & 1 & \cellcolor[HTML]{FFFFC7}34 & \cellcolor[HTML]{FFFFC7}27 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.68 & 0.81 & 0.77 & 0.80 & \cellcolor[HTML]{ACDDAA}0.82 & \cellcolor[HTML]{ACDDAA}0.45 & 0.80 & 0.60 & 0.69 & 0.90 & 0.75 & 0.00 & \cellcolor[HTML]{FFFFC7}0.71 & \cellcolor[HTML]{FFFFC7}0.89 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$ \\ p = 0.2073\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$ \\ p = 0.4947\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 82) = 5.137$ \\ p = 0.0117\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$ \\ p= 0.1709\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$ \\ p =0.078\end{tabular}} \\ \cline{2-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}39 & \cellcolor[HTML]{ACDDAA}89 & \cellcolor[HTML]{ACDDAA}91 & \cellcolor[HTML]{ACDDAA}37 & \cellcolor[HTML]{FFFFC7}88 & \cellcolor[HTML]{FFFFC7}39 & \cellcolor[HTML]{FFFFC7}4 & \cellcolor[HTML]{FFFFC7}4 & \cellcolor[HTML]{FFFFC7}12 & \cellcolor[HTML]{FFFFC7}53 & \cellcolor[HTML]{FFFFC7}49 & \cellcolor[HTML]{FFFFC7}6 & 33 & 58 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}0.69 & \cellcolor[HTML]{ACDDAA}0.84 & \cellcolor[HTML]{ACDDAA}0.86 & \cellcolor[HTML]{ACDDAA}0.65 & \cellcolor[HTML]{FFFFC7}0.84 & \cellcolor[HTML]{FFFFC7}0.72 & \cellcolor[HTML]{FFFFC7}1.00 & \cellcolor[HTML]{FFFFC7}0.75 & \cellcolor[HTML]{FFFFC7}0.75 & \cellcolor[HTML]{FFFFC7}0.85 & \cellcolor[HTML]{FFFFC7}0.80 & \cellcolor[HTML]{FFFFC7}0.33 & 0.70 & 0.81 \\ \cline{3-17} 
\multicolumn{1}{|c|}{\multirow{-6}{*}{Believability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 58} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 119} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 120} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 57} & \cellcolor[HTML]{FFFFC7}{\color[HTML]{333333} 94} & \cellcolor[HTML]{FFFFC7}39 & \cellcolor[HTML]{FFFFC7}5 & \cellcolor[HTML]{FFFFC7}8 & \cellcolor[HTML]{FFFFC7}18 & \cellcolor[HTML]{FFFFC7}70 & \cellcolor[HTML]{FFFFC7}66 & \cellcolor[HTML]{FFFFC7}10 & 46 & 80 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.26} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.09} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.21} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.02} & \cellcolor[HTML]{FFFFC7}{\color[HTML]{333333} 0.13} & \cellcolor[HTML]{FFFFC7}0.26 & \cellcolor[HTML]{FFFFC7}0.00 & \cellcolor[HTML]{FFFFC7}0.00 & \cellcolor[HTML]{FFFFC7}0.11 & \cellcolor[HTML]{FFFFC7}0.10 & \cellcolor[HTML]{FFFFC7}0.20 & \cellcolor[HTML]{FFFFC7}0.40 & 0.11 & 0.18 \\ \cline{3-17} 
\multicolumn{1}{|c|}{\multirow{-6}{*}{Desirability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$ \\ p = 0.0034\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$ \\ p = 0.059\end{tabular}}} & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$ \\ p= 0.0729\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$ \\ p = 0.2288\end{tabular}} \\ \hline

@@

Our study examined episodic processing in metric-specific groups, as well as the performance overall. Our study shows that comparing to static street-view images, recollection of event-driven memories using \textit{Rewind} videos is significantly improved for trips taken that were 100 - 1,000 km (62 - 620 miles) away from home by 50\%, $\chi^2(1, N=20) = 3.215$, $p <.05$; and for trips that were least frequently taken by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.

@@

\subsubsection{Travel Companions}
% trip accompanies have siginificant effects on both location and trip rememberance. 
% location rememberance: travel alone -  100%, not alone - 55%, $\chi^2(1,94) = 31.812$, p < 0.01
% trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
Our study shows that both location and trip remembrances are influenced by the presence of travel companions, yet in a opposite way. For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compare to 55\% rate reported by participants who believed that they traveled in groups, with $\chi^2(1,94) = 31.812$, $p < 0.00001$. On the other hand, trip details tend to be more easily remembered during accompanied visits. Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching a \textit{Rewind} video, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1,133) = 9.016$, p = 0.0013 $(< 0.01)$.

>>>>

% heather - add more results in here since we have more to report. Probably cut down image manipulation?
\begin{abstract}
We introduce Rewind system which assists in the recall of semantic and episodic memory by automatically recreating interactive sceneries of past trips. Rewind system uses historical geolocation data to generate egocentric videos of earlier experiences from publicly-available street side images. Since the effectiveness of memory cues is determined by their level of integration with the target memory, images used in Rewind system are manipulated to incorporate time-of-day, seasonal and weather information, thereby creating more faithful representation of the original experience. Users can interactively go back and forth in time by scrubbing over the video. Together, the composed video offer users a window into past travels. We report the results of a user study with eighteen participants conducted to collect location data over two weeks. Trips taken in groups were more likely to be recalled using Rewinds than trips taken alone. Rewind also serves as an experiment of the extreme scenario where users can freely roam and experience the world, keeping their mobile devices in their pockets, and still preserve believable representations that capture the past.
\end{abstract}

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 19 & 67 & 61 & 25 & \cellcolor[HTML]{ACDDAA}71 & \cellcolor[HTML]{ACDDAA}11 & 5 & 5 & 13 & 30 & 32 & 1 & 34 & 27 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.68 & 0.81 & 0.77 & 0.80 & \cellcolor[HTML]{ACDDAA}0.82 & \cellcolor[HTML]{ACDDAA}0.45 & 0.80 & 0.60 & 0.69 & 0.90 & 0.75 & 0.00 & 0.71 & 0.89 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$ \\ p = 0.2073\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$ \\ p = 0.4947\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 82) = 5.137$ \\ p = 0.0117\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$ \\ p= 0.1709\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$ \\ p =0.078\end{tabular}} \\ \cline{2-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}39 & \cellcolor[HTML]{ACDDAA}89 & \cellcolor[HTML]{ACDDAA}91 & \cellcolor[HTML]{ACDDAA}37 & 88 & 39 & 4 & 4 & 12 & 53 & 49 & 6 & 33 & 58 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}0.69 & \cellcolor[HTML]{ACDDAA}0.84 & \cellcolor[HTML]{ACDDAA}0.86 & \cellcolor[HTML]{ACDDAA}0.65 & 0.84 & 0.72 & 1.00 & 0.75 & 0.75 & 0.85 & 0.80 & 0.33 & 0.70 & 0.81 \\ \cline{3-17} 
\multicolumn{1}{|c|}{\multirow{-6}{*}{Belivability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 58} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 119} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 120} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 57} & 94 & 39 & 5 & 8 & 18 & 70 & 66 & 10 & 46 & 80 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.26} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.09} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.21} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.02} & 0.13 & 0.26 & 0.00 & 0.00 & 0.11 & 0.10 & 0.20 & 0.40 & 0.11 & 0.18 \\ \cline{3-17} 
\multicolumn{1}{|c|}{\multirow{-6}{*}{Desirability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$ \\ p = 0.0034\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$ \\ p = 0.059\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$ \\ p= 0.0729\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$ \\ p = 0.2288\end{tabular}} \\ \hline

@@

Our study examined episodic processing in metric-specific groups, as well as the performance overall. Our study shows that comparing to static street-view images, recollection of event-driven memories using Rewinds is significantly improved for trips taken that were 100 - 1,000 km (62 - 620 miles) away from home by 50\%, $\chi^2(1, N=20) = 3.215$, $p <.05$; and for trips that were least frequently taken by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.

@@

\subsubsection{Travel Companions}
% trip accompanies have siginificant effects on both location and trip rememberance. 
% location rememberance: travel alone -  100%, not alone - 55%, $\chi^2(1,94) = 31.812$, p < 0.01
% trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
Our study shows that both location and trip remembrances are influenced by the presence of travel companions, yet in a opposite way. For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compare to 55\% rate reported by participants who believed that they traveled in groups, with $\chi^2(1,94) = 31.812$, $p < 0.00001$. On the other hand, trip details tend to be more easily remembered during accompanied visits. Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1,133) = 9.016$, p = 0.0013 $(< 0.01)$.
